Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-25 snapshot_system/fast14_deduplication.tex
adjusted figures
revision

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
                \legend{$N_o$,
                    %$N_1+N_2$,
                    $N_1$,
                    $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

>>>>

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by the VM.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north east,
                legend style={
                    at={(1,0.825)},
                    anchor=north east
                },
                %legend columns=3
		]
                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
                \legend{$N_o$,
                    %$N_1+N_2$,
                    $N_1$,
                    $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
